### 2018-09-10 introduction.tex
@achubbz comment implemented

In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
elements}F$_3$) combine with carrier salts to form a liquid fuel that 
circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
Immediate advantages over traditional, solid-fueled, reactors include 
near-atmospheric pressure in the primary loop, 
relatively high coolant temperature, outstanding neutron economy, improved 
safety parameters, reduced fuel preprocessing, and the ability to continuously 
remove fission products and add fissile and/or fertile elements 
\cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
early 1970s by \gls{ORNL} to explore specifically the promise of the thorium 
fuel cycle, which uses natural thorium instead of enriched uranium. With 
continuous fuel reprocessing, the \gls{MSBR} realizes the advantages of the 
thorium fuel cycle because the $^{233}$U bred from 
$^{232}$Th is almost instantly\footnote{\space $^{232}$Th transmutes into 
$^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
($\tau_{1/2}$=26.967d).} recycled back into the core 
\cite{betzler_modeling_2016}. The chosen fuel salt, LiF-BeF$_2$-ThF$_4$-UF$_4$, has a 
melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
and good flow and heat transfer properties \cite{robertson_conceptual_1971}. In 
the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity 
of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. 
Finally, the \gls{MSR} also could be employed as a converter reactor for 
transmutation of spent fuel from current \glspl{LWR}.

>>>>

In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
elements}F$_3$) combine with carrier salts to form a liquid fuel that 
circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
Immediate advantages over traditional, solid-fueled, reactors include 
near-atmospheric pressure in the primary loop, 
relatively high coolant temperature, outstanding neutron economy, improved 
safety parameters, reduced fuel preprocessing, and the ability to continuously 
remove fission products and add fissile and/or fertile elements 
\cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
early 1970s by \gls{ORNL} to explore specifically the promise of the thorium 
fuel cycle, which uses natural thorium instead of enriched uranium. With 
continuous fuel reprocessing, the \gls{MSBR} realizes the advantages of the 
thorium fuel cycle because the $^{233}$U bred from 
$^{232}$Th is almost instantly\footnote{\space $^{232}$Th transmuted into 
$^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
($\tau_{1/2}$=26.967d).} recycled back into the core 
\cite{betzler_modeling_2016}. The chosen fuel salt, LiF-BeF$_2$-ThF$_4$-UF$_4$, has a 
melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
and good flow and heat transfer properties \cite{robertson_conceptual_1971}. In 
the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity 
of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. 
Finally, the \gls{MSR} also could be employed as a converter reactor for 
transmutation of spent fuel from current \glspl{LWR}.
